---
title: "STATISTICAL COMPUTING QUARTO"
format: html
editor: visual
---

## Statistical Computing Prac One

### Question 1

Let's access the air quality data set

```{r}
df <- (airquality)
View(df)
```

Now, find all the rows in the air quality data set that have missing values

```{r}
rows_missing <- which(rowSums(is.na(df)) > 0)
rows_missing
```

### Question 2

Find mean, sd, min, and max for each of temp and ozone level

```{r}
mean(df$Temp); sd(df$Temp); min(df$Temp); max(df$Temp)
```

Remove rows with missing values to calculate for ozone

```{r}
new_df <- na.omit(df)
mean(new_df$Ozone); sd(new_df$Ozone); min(new_df$Ozone); max(new_df$Ozone)
```

### Question 3

Linear regression with cars data set and calculating beta estimates

```{r}
View(cars)
y <- cars$speed
x <- model.matrix(~ dist, cars)
beta_hat <- (solve(t(x) %*% x)) %*% t(x) %*% y
beta_hat
```

### Question 4

Check that beta estimates are same as when fitting with lm() function

```{r}
q4 <- lm(speed ~ dist, cars)
q4
```

They are the same. Yay!
